Fusion Moves for Correlation Clustering

### 2014-11-14 paper/introduction-new.tex
fixed all changes where i knew the fix to

%!TEX root = ./egpaper_for_review.tex
%
\section{Introduction}
Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012},
see Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph.

>>>>

%!TEX root = ./egpaper_for_review.tex
%
\section{Introduction}
Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
See Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph.
